### 2015-04-20 whoop.tex
updated toolchain figure

The main aim of this phase is to take an input Linux driver written in C, together with an environmental model, and output an over-approximated version of the program in Boogie IVL, a simple imperative language with well-defined verification-focused semantics used as the input to a number of cutting-edge verifiers (e.g. Boogie and \corral). To achieve this translation, \whoop uses three LLVM\footnote{http://llvm.org}-based tools: Chauffeur\footnote{https://github.com/mc-imperial/chauffeur}, Clang\footnote{http://clang.llvm.org} and SMACK\footnote{https://github.com/smackers/smack}~\cite{rakamaric2014smack}.

@@

The Engine component of \whoop (see Figure~\ref{fig:whoop}) is responsible for parsing, instrumenting and sequentializing the abstract Boogie program. During the initial parsing, \whoop performs a static analysis (on the Boogie IVL code) to identify all lock identifiers and rewrite them to a unique constant Boogie variable, e.g. the following call to \texttt{mutex\_lock()}:

@@

\whoop is a sound but potentially imprecise static data race analyzer.  While developers do appreciate soundness, it is more important to ensure they are not overwhelmed by countless reports of false bugs.  Hence, to improve precision, we enable an external precise bug-finder for concurrent programs to be plugged into \whoop. The race-related information generated by \whoop can then be used to accelerate the bug-finder.  Currently, we support \corral~\cite{lal2012corral}, a state-of-the-art scalable bug-finder used by Microsoft to analyze Windows device drivers. \corral accepts Boogie IVL and hence it was easy to integrate into our tool flow. Our technique, though, is general and capable of accelerating any arbitrary bug-finder for concurrent programs.

>>>>

The aim of this phase (see Figure~\ref{fig:whoop} -- A) is to take an input Linux driver written in C, together with an environmental model, and output an over-approximated version of the program in Boogie IVL, a simple imperative language with well-defined verification-focused semantics used as the input to a number of cutting-edge verifiers (e.g. Boogie and \corral). To achieve this translation, \whoop uses three LLVM\footnote{http://llvm.org}-based tools: Chauffeur\footnote{https://github.com/mc-imperial/chauffeur}, Clang\footnote{http://clang.llvm.org} and SMACK\footnote{https://github.com/smackers/smack}~\cite{rakamaric2014smack}.

@@

The core \whoop tool (see Figure~\ref{fig:whoop} -- B) is responsible for parsing, instrumenting and sequentializing the abstract Boogie program. During the initial parsing, \whoop performs a static analysis (on the Boogie IVL code) to identify all lock identifiers and rewrite them to a unique constant Boogie variable, e.g. the following call to \texttt{mutex\_lock()}:

@@

\whoop is a sound but potentially imprecise static data race analyzer.  While developers do appreciate soundness, it is more important to ensure they are not overwhelmed by countless reports of false bugs.  Hence, to improve precision, we enable an external precise bug-finder for concurrent programs to be plugged into \whoop. The race-related information generated by \whoop can then be used to accelerate the bug-finder.  Currently, we support \corral~\cite{lal2012corral}, a state-of-the-art scalable bug-finder used by Microsoft to analyze Windows device drivers. \corral accepts Boogie IVL and hence it was easy to integrate into our toolchain (see Figure~\ref{fig:whoop} -- C). Our technique, though, is general and capable of accelerating any arbitrary bug-finder for concurrent programs.
